---
title: "Simple document"
author: Yu He
date: 2021-09-22
output:
  html_document:
   toc: TRUE
   toc_float: TRUE
   code_folding: hide
---

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

Let's write a new code chunk

This code chunk inmports the 'tidyverse', create a data frame, and make a histogram

```{r}
library(tidyverse)

set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = 0.5),
  y = 1 + 2 * x + rnorm(1000)
)


ggplot(plot_df, aes(x = x)) + geom_histogram()
```

# Learning assessment

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. 

```{r}
set.seed(12)

learning_df = 
  tibble(
    sample = rnorm(500, mean = 1),
    gr_than_0 = sample > 0,
    abs_val = abs(sample)
  )

ggplot(learning_df, aes(x = abs_val)) + geom_histogram()
```

